Distributed Topology Discovery in Self-Assembled Nano Networks

### 2014-02-18 PAPER/introduction.tex
Removed typos

\begin{figure*}
\centering
\begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
 (a) & (b)
 \end{tabular}
  \caption{(a) DNA tag matching and (b) resulting irregular topology}
  \label{fig:nana}
\end{figure*}
These aspects of a DNA self-assembly process lead to some important
implications to be addressed when approaching to the design of
a computer architecture: computational model should be based on a
distributed network of small processing and storage nodes, randomly
placed and interconnected (see Figure~\ref{fig:nana}-b).
Proof-of-concept of such architectures can be found for
example in~\cite{patwardhan2006_1}, where instruction and data
operands are move around the network in order to be processed.
Independently from the particular policy chosen for routing packets,
such networks must be able to guarantee deadlock freedom without any
prior assumption on topology.

In this work we introduce \disr{}, a Distributed Segment-based approach
to deadlock freedom in large scale DNA self assembled networks. Our
contribution aims to achieve the classical properties of a
segment-based approach~\cite{mejia_ipdps06} without requiring any
topology graph, external defect map or centralized algorithm
execution.  So the \disr{} approach is not intended to discover the
``optimal'' segment choice (ideally reachable with the knowledge of
the topology graph) but just to demonstrate a concrete model that can
fit into such complex, irregular and large sized networks.
It is important to
underline that, although we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architecture.

The paper is organized as follows: in Section~\ref{sec:related_works}
we summarize the main approaches to topology agnostic routing. Next in
Section~\ref{sec:disr_concepts} are described the main elements and
the execution model of the proposed approach.  In Section~\ref{sec:simulation}
simulations are carried out with the open-source tool Nanoxim to
demonstrate how \disr{} preserves some of the main segment-based
properties and how compares to the tree-based approaches. Finally a
draft of a architectural implementation is shown in
Section~\ref{sec:implementation} to evaluate the feasibility of the
approach in terms of node complexity.

>>>>

\begin{figure*}
\centering
\begin{tabular}{cc}
    \includegraphics[width=0.40\textwidth]{pictures/dna2b.eps} &
    \includegraphics[width=0.40\textwidth]{pictures/dna1_complex2.eps} \\
 (a) & (b)
 \end{tabular}
  \caption{(a) DNA tag matching and (b) resulting irregular topology}
  \label{fig:nana}
\end{figure*}
These aspects of a DNA self-assembly process lead to some important
implications to be addressed when approaching to the design of
a computer architecture: computational model should be based on a
distributed network of small processing and storage nodes, randomly
placed and interconnected (see Figure~\ref{fig:nana}-b).
Proof-of-concept of such architectures can be found for
example in~\cite{patwardhan2006_1}, where instruction and data
operands are moved around the network in order to be processed.
Independently of the particular policy chosen to route packets,
such networks must be able to guarantee deadlock freedom without any
prior assumption on topology.

In this work, we introduce \disr{}, a Distributed Segment-based approach
to deadlock freedom in large scale DNA self-assembled networks. Our
contribution aims to achieve the classical properties of a
segment-based approach~\cite{mejia_ipdps06} without requiring any
topology graph, external defect map or centralized algorithm
execution.  So the \disr{} approach is not intended to discover the
``optimal'' segment choice (ideally reachable with the knowledge of
the topology graph) but just to demonstrate a concrete model that can
fit into such complex, irregular and large sized networks.
It is important to
underline that, although we can assume an architecture similar to the
one depicted in Figure~\ref{fig:nana} as background, the topology discovery
problem faced in this work is more general and not strictly dependent on any of the
underlying computing architectures.

The paper is organized as follows: in Section~\ref{sec:related_works}
we summarize the main approaches for topology agnostic routing. Next, in
Section~\ref{sec:disr_concepts} are described the main elements and
the execution model of the proposed approach. In Section~\ref{sec:simulation},
simulations are carried out with the open-source tool Nanoxim to
demonstrate how \disr{} preserves some of the main segment-based
properties and how compares to the tree-based approaches. Finally a
draft of an architectural implementation is shown in
Section~\ref{sec:implementation} to evaluate the feasibility of the
approach in terms of node complexity.
